%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass{tccv_Eyal}
\usepackage[english]{babel}
\usepackage{lipsum, babel}

\begin{document}
\partEyal{Eyal Itskovits}
          {Experienced computational scientist and manager.}

\personal
    {Kharkap st. 52, Jerusalem}
    {054-2332640}
    {Eyal.x.itskovits@gsk.com}

\section{Professional Experience}
\begin{yearlistII}
\item{2024-Current}
    {Director of Machine Learning and Artificial Intelligence}
    {Leading GSK Flagship AI Scientist project}
    {Leading a multi-team, globally distributed project, with direct reporting and engagement with GSK's Global Leadership Team and Board.}
\item{2021-2024}
    {Senior AIML Research Engineer and Team Leader}
    {Team leading, AIML Reserch}
    {Lead a team of five PhD-level researchers applying cutting-edge machine learning to solve challenging problems in oncology}
\item{2007-2009}
     {Developer at OpTier}
     {Software development and reverse engineering}
     {Information security related product development and reverse engineering.}
\end{yearlistII}

\section{Academic experience}
\begin{eventlist}
\item{March 2013 -- January 2020}
     {PhD Candidate }
     {Prof. Alon Zaslaver's Group:}
I have been working on research questions dealing with neural encoding of complex stimuli, and with learning and memory in compact neural networks (See \textit{publications} section).

%\item{October 2011 -- August 2012}
%     {Undgergraduate lab member, and Computational Biology project}
%     {Prof. Ran Nathan's Movement Ecology Lab}
%
%Development of a classification system for freely moving vultures based on temporal acceleration signals.

\end{eventlist}


\section{Education}
\begin{yearlist}
\item{2015-2020}
     {Computer Science and Computational Biology, PhD}
     {Systems Neuroscience}
\item{2013-2015}
     {Computer Science and Computational Biology, MSc}
     {gpa: 93}
\item{2009-2012}
     {Computer Science and Computational Biology, BSc}
     {gpa: 90}
\end{yearlist}


\section{Skills}
\subsection{Data Analysis, Machine Learning and Software Engineering}
Practical and theoretical experience with:
\begin{itemize}
    \item
    \textbf{Statistical machine learning}.
    \item
    \textbf{Deep-learning}.
    \item
    \textbf{Signal processing}, and \textbf{time-series} analysis.
    \item
    \textbf{Strong mathematical and statistical background.}

\end{itemize}
\subsection{Software Development}
\begin{itemize}
    \item
    Experience with design and implementation of small and large software projects
    \item
    Proficient in \textbf{C}, \textbf{C++}, \textbf{Python}. Experience with server, desktop and web applications.
    \item
    Experience with \textbf{operation systems} internals. A strong expertise with \textbf{Linux} environments and \textbf{cloud computing}.
\end{itemize}
\subsection{Life Sciences}
\begin{itemize}
    \item
    Experience with various \textbf{molecular biology} procedures.
    \item
    Experience with advanced \textbf{optical systems}.
    \item
    Analysis of \textbf{high-dimensional neural activity data}, and next-generation \textbf{RNA Sequencing}.
\end{itemize}

\section{Teaching Experience}
\begin{yearlistTeach}
\item{2014-2019}
     {Probability and Statistics for the Life Sciences}
     {Hebrew University - Course 72301}
\item{2013}
     {OOP - Object Oriented Programming}
     {Hebrew University - Course 67125}
\item{2012}
     {General Genetics}
     {Hebrew University - Course 72155}
\end{yearlistTeach}

\section{Professional Service}
\subsection{Journal Editorial Service}
\begin{itemize}
    \item
    Reviewing Editor, \textit{eLife} -- Board of Reviewing Editors, 2026--present
\end{itemize}
\subsection{Conference Reviewer}
\begin{itemize}
    \item
    Neural Information Processing Systems (NeurIPS), 2024
    \item
    International Conference on Learning Representations (ICLR) -- ML For Drug Discovery Workshop, 2023
\end{itemize}

%\section{Publications}
%Itskovits, E., Levine. A, Cohen, E. and Zaslaver, A.
%\textbf{"A Novel Multi-Animal Tracker for Studying Complex Behaviors"}. Accepted. BMC Biology.
%\newline

%Azulay, Aharon, Eyal Itskovits, and Alon Zaslaver. 2016.\textbf{ "The \textit{C. Elegans} Connectome %Consists of Homogenous Circuits with Defined Functional Roles."} PLoS Computational Biology 12 (9)
%\newline

%Submitted (Equal Contribution): \newline
%Diptendu Mukherjee, Bogna Marta Ignatowska-Jankowska, Eyal Itskovits, Ben Jerry Gonzales, Hagit Turm, %Liz Izakso, Doron Haritan, Noa Bleistein, Chen Chen, Ido Amit,  Tal Shay, Brad Grueter, Alon Zaslaver %and Ami Citri
%\textbf{"Unique Transcriptional Signatures Encodes Salient Experiences in the Brain"}.
%\newline

%Manuscript in preparation: \newline
%Eyal Itskovits, Rotem Ruach, Alon Zaslaver
%\textbf{"Neural Pulses Code Chemical Gradients Dictating Chemotaxis Strategy"}.
%\newpage

\section{Honors and Awards}
\begin{itemize}
\item
UK Global Talent Endorsement (Exceptional Promise) - Royal Academy of Engineering - 2026
\item
London Tech Week 2026 - Invited Speaker
\item
JBC Postdocotral Fellowship - 2020
\item
HHMI Janelia's Junior Scientist Workshop on Machine Learning and Computer Vision participant - 2019
\item
Next-Gen Neuro Workshop for Advanced PhD Students participant - 2019
\item
The Irene and Michael Mochrik Award
For Outstanding Genetics Students - 2018
\item
SMART Award, Alexander Silverman Insititute of Life Sciences - 2018
\item
Excellent Teaching Assistant - 2013-2016, 2018-2019
\item
JBC Golden PhD Scholarship - 2017
\item
Best Poster - I-Core Single Molecule Biophysics Conference - 2015
\item
JBC Travel Scholarship - 2015
\item
Honorable Mention for poster - International Worm Meeting - 2015
\item
Mada - Life Sciences Excellence Program - 2013
\item
Dean's List - 2010-2012, 2013-2015
\end{itemize}


\section{Previous academic experience}
\begin{eventlist}
\item{October 2013 -- March 2013}
     {MSc Student}
     {Rotational Student}

\textbf{\textit{Prof. Sagiv Shifman's Lab}} - I analysed large-scale datasets of individuals with autistism spectrum disorder (ASD)  in search of the genomic correlates of the syndrome.
\newline\newline
\textbf{\textit{Prof. Nir Friedman's Lab}} - I studied a novel gene-regulation mechanism.

\item{October 2011 - October 2012}
     {BSc Student}
     {Movement Ecology Lab}

     I used machine learning to classify animal behavior using accelerator temporal signal.

%\item{October 2011 -- August 2012}
%     {Undgergraduate lab member, and Computational Biology project}
%     {Prof. Ran Nathan's Movement Ecology Lab}
%
%Development of a classification system for freely moving vultures based on temporal acceleration signals.

\end{eventlist}



\section{Volunteering}
\begin{factlist}
\item{2016-2017}
    {"Aleh" Running Team - Biweekly escorting of blind and visually impaired runners}
\item{2015-2017}
    {"Magdilim Rosh" - Exposing high school students to neuroscience research}
\item{2014}
     {"Exposure to Science" - Introducing research and basic science topics to adolescents from complex backgrounds}
\item{2011}
{"Magshimim Program" - Teaching computer science and information security to high school students from the social periphery  }
\end{factlist}

\section{Online profiles}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}
\begin{itemize}
    \item
    \href{https://scholar.google.co.il/citations?user=D36-7p8AAAAJ&hl=en}{\underline{Google Scholar}}
    \item
    \href{https://www.linkedin.com/in/eyal-itskovits-9b41a51/?originalSubdomain=il}{\underline{LinkedIn}}
    \item
    \href{https://twitter.com/itskov?lang=en}{\underline{Twitter}}
    \item
    \href{https://github.com/itskov}{\underline{GitHub}}
    \item
    \href{https://stackoverflow.com/users/931115/eyalitskovits}{\underline{StackOverflow}}
\end{itemize}


\vspace{-6pt} % Otherwise it just falls onto the next page.

\newpage
\onecolumn
\section{Publications}
\begin{itemize}
    \item
    Deshe, Noa, Yifat Eliezer, Lihi Hoch, \textbf{Eyal Itskovits}, Shachaf Ben-Ezra, and Alon Zaslaver. n.d. \\
    "Inheritance of Associative Memories in C. Elegans Nematodes." \\
    \textbf{BioRxiv}, https://doi.org/10.1101/2020.09.08.287318.
    \item
    Pritz, Chrisitian O., \textbf{Eyal Itskovits}, Eduard Bokman, Rotem Ruach, Vladimir Gritsenko, Tal Nelken, Mai Menasherof, Aharon Azulay, and Alon Zaslaver. n.d. \\
    "Principles for Coding Associative Memories in a Compact Neural Network." \\
    \textbf{BioRxiv}, https://doi.org/10.1101/2020.06.20.162818.
    \item
    Ishtayeh, Hasan, Hanna Achache, Eitan Kroizer, Yisrael Rappaport, \textbf{Eyal Itskovits}, Hila Gingold, Corinne Best, Oded Rechavi, and Yonatan B. Tzur. 2020. \\
    "Systematic Analysis of Long Intergenic Non-Coding RNAs in Germline Uncovers Roles in Somatic Growth." \\
    \textbf{RNA Biology}, September, 1–11.
    \item
    Iwanir, Shachar, Rotem Ruach, \textbf{Eyal Itskovits}, Christian O. Pritz, Eduard Bokman, and Alon Zaslaver. 2019. \\ "Irrational Behavior in C. Elegans Arises from Asymmetric Modulatory Effects within Single Sensory Neurons." \\
    \textbf{Nature Communications} 10 (1): 3202.
    \item
    \textbf{Itskovits, Eyal}, Rotem Ruach, and Alon Zaslaver. 2018. \\
    "Concerted Pulsatile and Graded Neural Dynamics Enables Efficient Chemotaxis in C. Elegans." \\
    \textbf{Nature Communications} 9 (1): 2866.
    \item
    Mukherjee, Diptendu, Bogna Marta Ignatowska-Jankowska, \textbf{Eyal Itskovits}, Ben Jerry Gonzales, Hagit Turm, Liz Izakson, Doron Haritan, et al. 2018. \\
    "Salient Experiences Are Represented by Unique Transcriptional Signatures in the Mouse Brain." \\
    \textbf{eLife} 7 (February). https://doi.org/10.7554/eLife.31220. \textbf{(Joint first author)}
    \item
    \textbf{Itskovits, Eyal}, Amir Levine, Ehud Cohen, and Alon Zaslaver. 2017. \\
    "A Multi-Animal Tracker for Studying Complex Behaviors." \\
    \textbf{BMC Biology} 15 (1): 29.
    \item
    Azulay, Aharon, \textbf{Eyal Itskovits}, and Alon Zaslaver. 2016. \\
    "The C. Elegans Connectome Consists of Homogenous Circuits with Defined Functional Roles." \\
    \textbf{PLoS Computational Biology} 12 (9): e1005021.
    \item
    Bean, Angela, Assaf Weiner, Amanda Hughes, \textbf{Eyal Itskovits}, Nir Friedman, and Oliver J. Rando. n.d. \\
    "Genome-Wide Histone Modification Patterns in Kluyveromyces Lactis Reveal Evolutionary Adaptation of a Heterochromatin-Associated Mark." \\
    \textbf{BioRxiv}, https://doi.org/10.1101/039776.
\end{itemize}


\end{document}
